---
title: "Fragment Analysis & Somatic Instability Report"
author: "`r config$key_variables$primary_group_var %||% 'Automated Pipeline'`"
date: "`r format(Sys.time(), '%B %d, %Y at %H:%M')`"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    toc_depth: 3
    code_folding: hide
    self_contained: true
---

```{r setup, include=FALSE}
# ========================================================================= #
# SECTION 1: CONFIGURATION & ENVIRONMENT
# ========================================================================= #
# config, modeling_data, all_model_outputs, and plot_database are passed in
# by Script 06 via knitr::knit() with envir=. No .RData loading needed here.

knitr::opts_chunk$set(
  echo      = FALSE,
  warning   = FALSE,
  message   = FALSE,
  fig.width = 10,
  fig.height = 7,
  out.width.px = 800
)

options(out.width.px = 800)

# --- Libraries ---
suppressPackageStartupMessages({
  library(tidyverse)
  library(patchwork)
  library(knitr)
  library(kableExtra)
  library(plotly)
  library(DT)
  library(htmltools)
  library(ragg)
})

# =========================================================================
# USER CONTROL PANEL
# Adjust these to customise which sections appear in the report.
# =========================================================================
vars_to_include   <- NULL           # NULL = all; or e.g. c("mode_change", "instability_index_change")
show_trend        <- TRUE           # Modeled expansion trajectory
show_slopes       <- TRUE           # Per-group expansion rates
show_waterfall    <- TRUE           # BLUP-ranked responder plot
show_qc_tabs      <- TRUE           # QC & diagnostics sub-tab
show_stat_tables  <- TRUE           # Interactive statistical tables
show_extra_tables <- TRUE           # QC_Clone_Differences, Rate_Comparisons, BLUPs table
plotly_height     <- 500            # px height for plotly widgets

# =========================================================================
# SECTION 2: ENVIRONMENT VALIDATION
# =========================================================================
# Abort early with informative messages rather than cryptic downstream errors.

required_objects <- c("config", "plot_database", "all_model_outputs",
                       "response_vars", "response_labels", "response_shortnames",
                       "output_dir")
missing_objects <- required_objects[!sapply(required_objects, exists)]
if (length(missing_objects) > 0) {
  stop(paste(
    "REPORT ERROR: The following objects were not found in the environment.\n",
    "Ensure Script 06 passes them correctly:\n",
    paste(" -", missing_objects, collapse = "\n")
  ))
}

# =========================================================================
# SECTION 3: BUILD PLOT REGISTRY
# =========================================================================
# Mirrors the logic in Script 04, kept here so the report is self-contained.
# All patterns match the actual plot_database keys produced by Script 02.

all_plots <- list(descriptive = list(), modeling = list(), qc = list(), exploratory = list())

if (exists("plot_database") && length(plot_database) > 0) {
  nms <- names(plot_database)
  
  # FIX: corrected prefixes to match actual Script 02 keys
  # Script 02 uses "01_avg_", "02_detail_", "03_profiles_" NOT "p_avg", "p_detail", "p_profiles"
  all_plots$descriptive  <- plot_database[grep("^p_avg_|p_detail_|p_profiles_|^p_heatmap_|^p_raincloud_", nms)]
  all_plots$modeling     <- plot_database[grep("^p_preds_|^p_overall_|^p_waterfall_", nms)]
  all_plots$qc           <- plot_database[grep("^p_qc_|^p_clone_het_|^p_volcano_", nms)]
  all_plots$exploratory  <- plot_database[grep("^p_cross_corr", nms)]
  
  # Uncategorised catch-all (makes new plots visible even if patterns aren't updated)
  known_keys <- c(
    names(all_plots$descriptive), names(all_plots$modeling),
    names(all_plots$qc), names(all_plots$exploratory)
  )
  uncategorised <- setdiff(nms, known_keys)
  if (length(uncategorised) > 0) {
    all_plots$other <- plot_database[uncategorised]
  }
}

# Pull loose exploratory objects from the environment (Script 03 outputs)
for (.obj in c("p_biplot", "p_scree", "p_loadings_bars", "p_corr_ggpairs_color")) {
  if (exists(.obj)) all_plots$exploratory[[.obj]] <- get(.obj)
}

# =========================================================================
# SECTION 4: RESOLVE ACTIVE RESPONSE VARIABLES
# =========================================================================
report_vars <- if (!is.null(vars_to_include)) {
  intersect(response_vars, vars_to_include)
} else {
  response_vars
}

if (length(report_vars) == 0) {
  stop("REPORT ERROR: No response variables to report. Check 'vars_to_include' and 'response_vars'.")
}

# =========================================================================
# SECTION 5: HELPER FUNCTIONS
# =========================================================================

# Render a ggplot as an interactive plotly widget, with graceful fallback.
safe_plotly <- function(p, height = plotly_height) {
  if (is.null(p)) {
    return(htmltools::div(
      class = "alert alert-warning",
      style = "font-size: 0.9em; padding: 8px 12px;",
      htmltools::tags$i(class = "fa fa-info-circle"),
      " Plot not available — may not have been generated for this experiment style."
    ))
  }
  if (inherits(p, "ggplot")) {
    tryCatch({
      p_int <- plotly::ggplotly(p, height = height) %>%
        plotly::layout(margin = list(b = 50, l = 60)) %>%
        plotly::config(displayModeBar = TRUE, displaylogo = FALSE,
                       modeBarButtonsToRemove = list("sendDataToCloud", "autoScale2d"))
      return(htmlwidgets::as_widget(p_int))
    },
      error = function(e) {
        # Create a temporary file path
        tmp_file <- tempfile(fileext = ".png")
        
        # Save the plot to the temp file
        ggplot2::ggsave(tmp_file, plot = p, width = 10, height = 7, dpi = 120, device = ragg::agg_png)
        
        # Fallback to static rendering
        htmltools::tagList(
          htmltools::p(style = "color: #888; font-size: 0.85em;",
                       "(Static image — interactive conversion not supported for this plot type.)"),
          htmltools::tags$img(
            src = knitr::image_uri(tmp_file),
            style = "max-width:100%;"
          )
        )
      }
    )
  } else {
    return(p)  # Already a plotly/htmlwidget
  }
}

safe_dt <- function(df, caption = NULL, page_length = 8) {
  # 1. Check if df is actually a data frame and has columns
  if (is.null(df) || !is.data.frame(df) || ncol(df) == 0 || nrow(df) == 0) {
    return(htmltools::p(style = "color: #888;", htmltools::em("No data available.")))
  }

  # 2. Clean 'Table-Breakers': Replace Inf/NaN with NA and ensure valid names
  df_clean <- df %>%
    dplyr::rename_with(~ ifelse(.x == "" | is.na(.x), paste0("V", seq_along(.x)), .x)) %>%
    dplyr::mutate(across(where(is.numeric), ~ ifelse(is.infinite(.x) | is.nan(.x), NA, .x))) %>%
    dplyr::mutate(across(where(is.numeric), ~ round(.x, 5)))

  # 3. Render with explicit fillContainer = FALSE 
  # Sometimes 'asis' loops struggle if the widget tries to fill a container that doesn't exist yet
  DT::datatable(
    df_clean,
    caption    = caption,
    rownames   = FALSE,
    filter     = "top",
    width      = "100%",
    height     = "auto", # Change from fixed to auto
    extensions = "Buttons",
    options    = list(
      pageLength = page_length,
      scrollX    = TRUE,
      autoWidth  = TRUE,
      dom        = "Bfrtip",
      buttons    = list("csv", "excel")
    )
  )
}

# Format a p-value with stars for inline display.
fmt_pval <- function(p) {
  if (is.null(p) || is.na(p)) return("—")
  stars <- dplyr::case_when(p < 0.001 ~ "***", p < 0.01 ~ "**", p < 0.05 ~ "*", TRUE ~ "ns")
  paste0(formatC(p, format = "e", digits = 2), " ", stars)
}

# Render a named list of tables as sub-sections.
render_table_list <- function(tbl_list, skip_patterns = NULL) {
  out <- list()
  for (tbl_name in names(tbl_list)) {
    if (!is.null(skip_patterns) && any(stringr::str_detect(tbl_name, skip_patterns))) next
    tbl <- tbl_list[[tbl_name]]
    if (!is.data.frame(tbl) || nrow(tbl) == 0) next
    friendly <- stringr::str_replace_all(tbl_name, "_", " ")
    out <- c(out, list(
      htmltools::h4(friendly, style = "color: #2c3e50; margin-top: 1.2em;"),
      safe_dt(tbl, caption = friendly)
    ))
  }
  if (length(out) == 0) return(htmltools::p(em("No tables available.")))
  htmltools::tagList(out)
}
```

---

## Experiment Overview {.unnumbered}

```{r experiment-summary}
# =========================================================================
# Experiment metadata card — rendered once at the top of the report
# =========================================================================
primary_var  <- config$key_variables$primary_group_var
time_var     <- config$key_variables$time_variable
secondary_var <- config$key_variables$secondary_group_var %||% "—"
re_cross      <- config$key_variables$optional_crossed_effect %||% "—"
exp_style     <- stringr::str_to_title(config$key_variables$experiment_style %||% "clone")

# Quick summary stats from modeling_data if available
n_groups <- n_reps <- n_timepoints <- "—"
if (exists("modeling_data") && !is.null(modeling_data)) {
  n_groups     <- dplyr::n_distinct(modeling_data[[primary_var]], na.rm = TRUE)
  n_timepoints <- dplyr::n_distinct(modeling_data[[time_var]], na.rm = TRUE)
  if (!is.null(secondary_var) && secondary_var != "—" && secondary_var %in% names(modeling_data)) {
    n_reps <- dplyr::n_distinct(modeling_data[[secondary_var]], na.rm = TRUE)
  }
}

htmltools::div(
  class = "well",
  style = "background: #f8f9fa; border-left: 4px solid #18bc9c; padding: 14px 18px; border-radius: 4px;",
  htmltools::tags$table(
    style = "width:100%; font-size: 0.95em;",
    htmltools::tags$tr(
      htmltools::tags$td(style = "width:50%; padding: 4px 0;",
        htmltools::tags$b("Experiment Style: "), exp_style),
      htmltools::tags$td(style = "padding: 4px 0;",
        htmltools::tags$b("Output Directory: "),
        htmltools::tags$code(style = "font-size: 0.85em;", output_dir))
    ),
    htmltools::tags$tr(
      htmltools::tags$td(style = "padding: 4px 0;",
        htmltools::tags$b("Primary Group: "), str_to_title(primary_var),
        htmltools::tags$span(style = "color: #888; margin-left: 6px;",
                             paste0("(", n_groups, " levels)"))),
      htmltools::tags$td(style = "padding: 4px 0;",
        htmltools::tags$b("Secondary Group: "), str_to_title(secondary_var))
    ),
    htmltools::tags$tr(
      htmltools::tags$td(style = "padding: 4px 0;",
        htmltools::tags$b("Time Variable: "), str_to_title(time_var),
        htmltools::tags$span(style = "color: #888; margin-left: 6px;",
                             paste0("(", n_timepoints, " timepoints)"))),
      htmltools::tags$td(style = "padding: 4px 0;",
        htmltools::tags$b("Batch / Crossed Effect: "), str_to_title(re_cross))
    ),
    htmltools::tags$tr(
      htmltools::tags$td(style = "padding: 4px 0;",
        htmltools::tags$b("Response Variables: "),
        paste(report_vars, collapse = ", ")),
      htmltools::tags$td(style = "padding: 4px 0;",
        htmltools::tags$b("Report Generated: "),
        format(Sys.time(), "%Y-%m-%d %H:%M"))
    )
  )
)
```

---

# Results by Variable {.tabset .tabset-pills}

```{r generate_tabs, results='asis'}
# =========================================================================
# SECTION 6: DYNAMIC PER-VARIABLE TABBED REPORT
# =========================================================================

for (var in report_vars) {

  short_var    <- response_shortnames[[var]] %||% var
  friendly_name <- response_labels[[var]] %||% stringr::str_to_title(var)
  model_outputs <- all_model_outputs[[var]]
  
  # Pull the group rates table for the inline summary card
  rates_tbl <- model_outputs$results_tables$Group_Expansion_Rates

  # -----------------------------------------------------------------------
  # TOP-LEVEL TAB HEADER
  # -----------------------------------------------------------------------
  cat(sprintf("\n\n## %s {.tabset}\n\n", friendly_name))

  # -----------------------------------------------------------------------
  # INLINE SUMMARY CARD (appears above the sub-tabs for quick orientation)
  # -----------------------------------------------------------------------
  if (!is.null(rates_tbl) && nrow(rates_tbl) > 0) {
    slope_col <- intersect(c("slope", "Slope", "Estimate", "emmean", "Expansion_Rate"), names(rates_tbl))[1]
    
    if (!is.na(slope_col)) {
      pval_col <- intersect(c("p.value", "P_Value", "P_Value_Adjusted"), names(rates_tbl))[1]
      
      if (!is.na(pval_col)) {
        n_sig <- sum(as.numeric(rates_tbl[[pval_col]]) < 0.05, na.rm = TRUE)
        max_slope <- rates_tbl %>%
          dplyr::slice_max(order_by = abs(.data[[slope_col]]), n = 1, with_ties = FALSE)
        
        card_html <- htmltools::div(
          style = "background:#eaf4fb; border-left:4px solid #3498db; padding:10px 15px; border-radius:4px; margin-bottom:1em; font-size:0.9em;",
          htmltools::tags$b(paste0("\u2139\ufe0f ", friendly_name, " — Quick Summary")),
          htmltools::tags$br(),
          sprintf(
            "%d group(s) with significant expansion (p < 0.05). Fastest group: %s (slope = %.4f per timepoint).",
            n_sig,
            as.character(max_slope[[names(rates_tbl)[1]]]),
            as.numeric(max_slope[[slope_col]])
          )
        )
        cat(as.character(card_html)) # Safely print standard HTML tags
      }
    }
  }

  # -----------------------------------------------------------------------
  # SUB-TAB 1: Trends & Trajectories
  # -----------------------------------------------------------------------
  cat("\n\n### Trends & Trajectories\n\n")
  
  p_avg_key  <- paste0("p_avg_", short_var)
  p_pred_key <- paste0("p_overall_2a_", short_var)
  if (is.null(all_plots$descriptive[[p_avg_key]])) p_avg_key <- paste0("p_preds_", short_var)
  
  cat("**Group Averages** \nMean ± SEM of the raw data per group.\n\n")
  cat(knitr::knit_print(safe_plotly(all_plots$descriptive[[p_avg_key]])))

  cat("\n\n<br><hr><br>\n\n**Modeled Expansion Trajectory** \nFitted LMER trajectories; controls for random effects of biological replicate.\n\n")
  cat(knitr::knit_print(safe_plotly(all_plots$modeling[[p_pred_key]])))

  p_rc_key <- paste0("p_raincloud_", short_var)
  if (!is.null(all_plots$descriptive[[p_rc_key]])) {
    cat("\n\n<br><hr><br>\n\n**Distribution Shift (Raincloud)** \nHalf-violin + boxplot + jitter showing how the population distribution shifts over time.\n\n")
    cat(knitr::knit_print(safe_plotly(all_plots$descriptive[[p_rc_key]])))
  }

  # -----------------------------------------------------------------------
  # SUB-TAB 2: Expansion Rates
  # -----------------------------------------------------------------------
  if (show_slopes) {
    cat("\n\n### Expansion Rates\n\n")
    
    p_slopes_key <- paste0("p_overall_2b_", short_var)
    if (is.null(all_plots$modeling[[p_slopes_key]])) {
      p_slopes_key <- paste0("p_preds_avg_", short_var)
    }
    
    cat("**Per-Group Expansion Rates (LMER-Estimated)** \nShows the modelled rate of change (slope) for each group with confidence intervals.\n\n")
    cat(knitr::knit_print(safe_plotly(all_plots$modeling[[p_slopes_key]])))
    
    if (!is.null(rates_tbl) && nrow(rates_tbl) > 0) {
      cat("\n\n<br>\n\n**Expansion Rate Summary** *(p < 0.05 = significant expansion)*\n\n")
      
      sig_col <- intersect(c("p.value", "P_Value", "P_Value_Adjusted"), names(rates_tbl))[1]
      tbl_display <- rates_tbl %>% dplyr::mutate(dplyr::across(where(is.numeric), ~round(.x, 4)))
      
      kbl_out <- kableExtra::kbl(tbl_display, format = "html", align = "r") %>%
        kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                                  full_width = FALSE, font_size = 13)
      
      if (!is.na(sig_col)) {
        sig_rows <- which(as.numeric(rates_tbl[[sig_col]]) < 0.05)
        if (length(sig_rows) > 0) {
          kbl_out <- kbl_out %>%
            kableExtra::row_spec(sig_rows, bold = TRUE, color = "white", background = "#18bc9c")
        }
      }
      cat(as.character(kbl_out)) # Safely print kable outputs
    }
  }

  # -----------------------------------------------------------------------
  # SUB-TAB 3: Individual Profiles
  # -----------------------------------------------------------------------
  cat("\n\n### Individual Profiles\n\n")
  
  p_waterfall_key     <- paste0("p_waterfall_", short_var)
  p_clone_trends_key  <- paste0("p_clone_trends_", short_var)
  p_rep_profiles_key  <- paste0("p_rep_profiles_", short_var)

  if (!is.null(all_plots$modeling[[p_waterfall_key]]) && show_waterfall) {
    cat("**Clonal Waterfall (BLUP-Ranked)** \nBiological replicates ranked by their True BLUP expansion rate. Reveals within-group heterogeneity.\n\n")
    cat(knitr::knit_print(safe_plotly(all_plots$modeling[[p_waterfall_key]])))
    cat("\n\n<br><hr><br>\n\n")
  }

  if (!is.null(all_plots$modeling[[p_clone_trends_key]])) {
    cat("**Clone Trajectories** \nIndividual clone-level longitudinal profiles overlaid per genotype.\n\n")
    cat(knitr::knit_print(safe_plotly(all_plots$modeling[[p_clone_trends_key]])))
    cat("\n\n<br><hr><br>\n\n")
  }

  if (!is.null(all_plots$modeling[[p_rep_profiles_key]])) {
    cat("**Biological Replicate Profiles** (Faceted by Clone)  \n\n")
    cat(knitr::knit_print(safe_plotly(all_plots$modeling[[p_rep_profiles_key]])))
  }

  # -----------------------------------------------------------------------
  # SUB-TAB 4: Quality Control
  # -----------------------------------------------------------------------
  if (show_qc_tabs) {
    cat("\n\n### Quality Control\n\n")
    
    p_volcano_key  <- paste0("p_volcano_", short_var)
    p_het_key      <- paste0("p_clone_het_", short_var)
    p_heatmap_key  <- paste0("p_heatmap_", short_var)
    
    qc_rendered <- FALSE

    if (!is.null(all_plots$qc[[p_volcano_key]])) {
      cat("**Volcano Plot (Rate Comparisons)** \nEffect size vs. statistical significance for pairwise group comparisons.\n\n")
      cat(knitr::knit_print(safe_plotly(all_plots$qc[[p_volcano_key]])))
      cat("\n\n<br><hr><br>\n\n")
      qc_rendered <- TRUE
    }
    
    if (!is.null(all_plots$qc[[p_het_key]])) {
      cat("**Clone Slope Heterogeneity** \nTests whether biological replicates within a genotype have significantly different expansion rates.\n\n")
      cat(knitr::knit_print(safe_plotly(all_plots$qc[[p_het_key]])))
      cat("\n\n<br><hr><br>\n\n")
      qc_rendered <- TRUE
    }
    
    if (!is.null(all_plots$descriptive[[p_heatmap_key]])) {
      cat("**Plate Heatmap** \nVisualises the per-well data across the plate layout to detect spatial batch effects.\n\n")
      cat(knitr::knit_print(safe_plotly(all_plots$descriptive[[p_heatmap_key]])))
      qc_rendered <- TRUE
    }
    
    p_slope_compare_key <- paste0("p_qc_slope_compare_", short_var)
    p_vis_shift_key     <- paste0("p_qc_vis_shift_", short_var)
    
    if (!is.null(all_plots$qc[[p_slope_compare_key]])) {
      cat("**Calculation Method QC** \nValidates the formal LMER model slope against a naive simple trendline.\n\n")
      cat(knitr::knit_print(safe_plotly(all_plots$qc[[p_slope_compare_key]])))
      cat("\n\n<br><hr><br>\n\n")
      qc_rendered <- TRUE
    }
    
    if (!is.null(all_plots$qc[[p_vis_shift_key]])) {
      cat("**Model Adjustment Shift** \nVisualises how much the LMER adjusted the raw replicate trajectories.\n\n")
      cat(knitr::knit_print(safe_plotly(all_plots$qc[[p_vis_shift_key]])))
      qc_rendered <- TRUE
    }

    if (!qc_rendered) {
      cat(as.character(htmltools::p(style = "color: #888;", htmltools::em("No QC plots available for this variable."))))
    }
  }

  # -----------------------------------------------------------------------
  # SUB-TAB 5: Statistical Tables
  # -----------------------------------------------------------------------
  if (show_stat_tables) {
    cat("\n\n### Statistical Tables\n\n")
    
    if (is.null(model_outputs) || is.null(model_outputs$results_tables)) {
      cat(as.character(htmltools::p(em("No model output found for this variable."))))
    } else {
      tbls <- model_outputs$results_tables
      
      priority_tables <- c("Group_Expansion_Rates", "Model_Coefficients",
                           "Rate_Comparisons", "Individual_Slopes_BLUPs")
      
      for (tbl_name in priority_tables) {
        if (!is.null(tbls[[tbl_name]]) && nrow(tbls[[tbl_name]]) > 0) {
          friendly <- stringr::str_replace_all(tbl_name, "_", " ")
          cat(sprintf("\n\n**%s**\n\n", friendly))
          # Instead of cat(knitr::knit_print(...))
          res <- safe_dt(tbls[[tbl_name]], caption = friendly)
          knitr::knit_print(htmltools::tagList(res))
          cat("\n\n<br>\n\n")
        }
      }
      
      if (show_extra_tables) {
        remaining <- setdiff(names(tbls), priority_tables)
        for (tbl_name in remaining) {
          tbl <- tbls[[tbl_name]]
          if (!is.data.frame(tbl) || nrow(tbl) == 0) next
          friendly <- stringr::str_replace_all(tbl_name, "_", " ")
          cat(sprintf("\n\n**%s** *(QC)*\n\n", friendly))
          res <- safe_dt(tbls[[tbl_name]], caption = friendly)
          knitr::knit_print(htmltools::tagList(res))
          cat("\n\n<br>\n\n")
        }
      }
    }
  }
  
} # end for (var in report_vars)

```

---

# Combined Analysis {.tabset .tabset-pills}

## Cross-Metric Correlation

Compares expansion rates (True BLUP slope) for **Modal CAG length** vs. **Instability Index**
across all biological replicates. A positive correlation indicates that clones expanding
fastest in modal CAG are also accumulating the most somatic instability.

```{r cross-corr, out.width="100%"}
p_cc <- all_plots$exploratory$p_cross_corr_mode_vs_iic
if (!is.null(p_cc)) {
  safe_plotly(p_cc, height = 550)
} else {
  htmltools::HTML("<p style='color:#888;'><em>Cross-correlation plot not generated &mdash; requires both modal and instability index variables to be modelled in Script 02.</em></p>")
}
```

## Principal Component Analysis

PCA reduces dimensionality across all measured variables to identify overarching patterns,
cluster structure, or batch effects.

```{r pca, out.width="100%"}
p_bp <- all_plots$exploratory$p_biplot
p_sc <- all_plots$exploratory$p_scree
p_ld <- all_plots$exploratory$p_loadings_bars

if (!is.null(p_bp)) {
  htmltools::h4("Biplot")
  htmltools::p("Points = biological replicates; arrows = variables driving separation.")
  safe_plotly(p_bp, height = 550)
} else {
  htmltools::HTML("<p style='color:#888;'><em>PCA biplot not available (Script 03 may not have been run, or n was too small).</em></p>")
}

if (!is.null(p_sc)) {
  htmltools::HTML("<br><hr><br>")
  htmltools::h4("Scree Plot")
  safe_plotly(p_sc, height = 350)
}

if (!is.null(p_ld)) {
  htmltools::HTML("<br><hr><br>")
  htmltools::h4("Variable Loadings")
  htmltools::p("Contribution of each variable to the first two principal components.")
  safe_plotly(p_ld, height = 400)
}
```

## Correlation Matrix

Pairwise relationships between all measured variables. Note: `ggpairs` composites cannot
be converted to interactive plotly — rendered as static image.

```{r corr-matrix, out.width="100%", fig.width=14, fig.height=14}
p_cm <- all_plots$exploratory$p_corr_ggpairs_color
if (!is.null(p_cm)) {
  print(p_cm)
} else {
  cat("*Correlation matrix not available.*")
}
```

---

# Pipeline Diagnostics {.tabset}

Plots generated during Script 01 data processing — independent of any single response variable.

## Replication QC

```{r rep-qc, out.width="100%"}
p_rc  <- plot_database[["p_qc_rep_counts"]]
p_rcb <- plot_database[["p_qc_rep_counts_bubble"]]

if (!is.null(p_rc)) {
  htmltools::h4("Replicate Count Summary")
  safe_plotly(p_rc, height = 450)
}
if (!is.null(p_rcb)) {
  htmltools::HTML("<br>")
  htmltools::h4("Replicate Count Bubble Plot")
  safe_plotly(p_rcb, height = 450)
}
if (is.null(p_rc) && is.null(p_rcb)) {
  cat("*No replication QC plots available.*")
}
```

## Hierarchical Legend

```{r legend, out.width="60%", fig.height=4}
p_leg <- plot_database[["p_hierarchical_legend"]]
if (!is.null(p_leg)) {
  print(p_leg)
} else {
  cat("*Legend plot not available.*")
}
```

---

# Session Info {.unnumbered}

```{r session-info, echo=TRUE}
sessioninfo::session_info()
```
