---
title: "Advanced Fragment Analysis & Instability Report"
author: "Automated Pipeline"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float: true
    toc_depth: 3
    code_folding: hide
    self_contained: true
---

```{r setup, include=FALSE}
# ========================================================================= #
# 1. REPORT CONFIGURATION & ENVIRONMENT PREP
# ========================================================================= #
# Note: config, modeling_data, all_model_outputs, and plot_database are 
# automatically passed in by Script 06. No need to load .RData here!

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 7)

library(tidyverse)
library(patchwork)
library(knitr)
library(kableExtra)
library(plotly)
library(DT)
library(htmltools)

# Specify which variables to include. Leave as NULL to include everything.
vars_to_include <- c("mode_change", "instability_index_change") 

# Toggle which plot types you want generated in the HTML:
show_averaged_trend  <- TRUE
show_faceted_slopes  <- TRUE
show_waterfall       <- TRUE
show_stat_tables     <- TRUE

# Build the all_plots database for easy access
all_plots <- list(descriptive = list(), modeling = list(), qc = list(), exploratory = list())

if (exists("plot_database")) {
  names_db <- names(plot_database)
  all_plots$descriptive <- plot_database[grep("^p_avg|^p_detail|^p_profiles|^p_heatmap|^p_raincloud", names_db)]
  all_plots$modeling <- plot_database[grep("^p_preds|^p_overall|^p_slopes|^p_clone_trends|^p_rep_profiles|^p_waterfall", names_db)]
  all_plots$qc <- plot_database[grep("^p_qc|^p_clone_het|^p_volcano", names_db)]
  all_plots$exploratory <- plot_database[grep("^p_cross_corr", names_db)]
}

# Pull in loose exploratory plots (PCA) from the environment if they exist
for (obj_name in c("p_biplot", "p_scree", "p_loadings_bars", "p_corr_ggpairs_color")) {
  if (exists(obj_name)) {
    all_plots$exploratory[[obj_name]] <- get(obj_name)
  }
}

# Filter variables based on your control panel
if (!is.null(vars_to_include)) {
  report_vars <- intersect(response_vars, vars_to_include)
} else {
  report_vars <- response_vars
}

# Helper function to safely render plotly without breaking non-compatible plots
safe_plotly <- function(p) {
  if (is.null(p)) return(htmltools::HTML("<em>Plot not available.</em><br><br>"))
  if (inherits(p, "ggplot")) {
    return(plotly::ggplotly(p) %>% plotly::layout(margin = list(b = 40)))
  }
  return(p)
}
```

## Experiment Summary
* **Experiment Style:** `r stringr::str_to_title(config$key_variables$experiment_style)`  
* **Primary Group (Genotype):** `r config$key_variables$primary_group_var`  
* **Output Directory:** `r output_dir`  

***

# Results by Variable {.tabset .tabset-pills}

```{r generate_dynamic_ui, results='asis'}
# ========================================================================= #
# 2. DYNAMIC REPORT GENERATOR (Nested Tabs)
# ========================================================================= #
out_tags <- list()

for (var in report_vars) {
  short_var <- response_shortnames[[var]] %||% var
  friendly_name <- response_labels[[var]] %||% stringr::str_to_title(var)
  
  # Top-Level Tab for the Variable
  out_tags <- append(out_tags, list(htmltools::HTML(paste0("\n\n## ", friendly_name, " {.tabset}\n\n"))))
  
  # -------------------------------------------------------------------------
  # SUB-TAB 1: Modeled Trends
  # -------------------------------------------------------------------------
  out_tags <- append(out_tags, list(htmltools::HTML("\n\n### Trends & Trajectories\n\n**Overall Modeled Trend**<br>Shows the modeled expansion trajectory over time, averaged across batches.<br><br>")))
  
  plot_trend <- paste0("p_overall_2a_", short_var)
  if (is.null(all_plots$modeling[[plot_trend]])) plot_trend <- paste0("p_preds_", short_var)
  out_tags <- append(out_tags, list(safe_plotly(all_plots$modeling[[plot_trend]]), htmltools::HTML("\n\n<br><br>\n\n")))
  
  plot_raincloud <- paste0("p_raincloud_", short_var)
  if (!is.null(all_plots$descriptive[[plot_raincloud]])) {
    out_tags <- append(out_tags, list(htmltools::HTML("**Distribution Shift (Raincloud)**<br>Shows how the population distribution changes across timepoints.<br><br>")))
    out_tags <- append(out_tags, list(safe_plotly(all_plots$descriptive[[plot_raincloud]]), htmltools::HTML("\n\n<br><br>\n\n")))
  }

  # -------------------------------------------------------------------------
  # SUB-TAB 2: Expansion Rates
  # -------------------------------------------------------------------------
  if (show_faceted_slopes) {
    out_tags <- append(out_tags, list(htmltools::HTML("\n\n### Expansion Rates\n\n**Calculated Expansion Slopes**<br>Shows the explicit rate of change, faceted by genotype and batch.<br><br>")))
    
    plot_slopes <- paste0("p_slopes_faceted_", short_var)
    if (is.null(all_plots$modeling[[plot_slopes]])) plot_slopes <- paste0("p_slopes_", short_var)
    out_tags <- append(out_tags, list(safe_plotly(all_plots$modeling[[plot_slopes]]), htmltools::HTML("\n\n<br><br>\n\n")))
  }
  
  # -------------------------------------------------------------------------
  # SUB-TAB 3: Responder Waterfall
  # -------------------------------------------------------------------------
  if (show_waterfall) {
    out_tags <- append(out_tags, list(htmltools::HTML("\n\n### Clonal Waterfall\n\n**Individual Responder Profiles**<br>Biological replicates ranked by their True BLUP expansion rate.<br><br>")))
    
    plot_wf <- paste0("p_waterfall_", short_var)
    out_tags <- append(out_tags, list(safe_plotly(all_plots$modeling[[plot_wf]]), htmltools::HTML("\n\n<br><br>\n\n")))
  }

  # -------------------------------------------------------------------------
  # SUB-TAB 4: Quality Control & Diagnostics
  # -------------------------------------------------------------------------
  out_tags <- append(out_tags, list(htmltools::HTML("\n\n### Quality Control\n\n")))
  
  plot_volcano <- paste0("p_volcano_", short_var)
  if (!is.null(all_plots$qc[[plot_volcano]])) {
    out_tags <- append(out_tags, list(htmltools::HTML("**Volcano Plot (Rate Comparisons)**<br>Effect size vs statistical significance for group comparisons.<br><br>")))
    out_tags <- append(out_tags, list(safe_plotly(all_plots$qc[[plot_volcano]]), htmltools::HTML("\n\n<br><hr><br>\n\n")))
  }
  
  plot_qc_slope <- paste0("p_qc_slope_compare_", short_var)
  if (!is.null(all_plots$qc[[plot_qc_slope]])) {
    out_tags <- append(out_tags, list(htmltools::HTML("**Calculation Method QC**<br>Validates the formal LMER model against a naive simple trendline.<br><br>")))
    out_tags <- append(out_tags, list(safe_plotly(all_plots$qc[[plot_qc_slope]]), htmltools::HTML("\n\n<br><hr><br>\n\n")))
  }
  
  plot_qc_shift <- paste0("p_qc_vis_shift_", short_var)
  if (!is.null(all_plots$qc[[plot_qc_shift]])) {
    out_tags <- append(out_tags, list(htmltools::HTML("**Model Adjustment Shift**<br>Visualizes how much the LMER adjusted the raw trajectories.<br><br>")))
    out_tags <- append(out_tags, list(safe_plotly(all_plots$qc[[plot_qc_shift]]), htmltools::HTML("\n\n<br><br>\n\n")))
  }

  # -------------------------------------------------------------------------
  # SUB-TAB 5: Statistical Tables
  # -------------------------------------------------------------------------
  if (show_stat_tables) {
    out_tags <- append(out_tags, list(htmltools::HTML("\n\n### Statistical Tables\n\n")))
    
    model_outputs <- all_model_outputs[[var]]
    if (!is.null(model_outputs) && !is.null(model_outputs$results_tables)) {
      
      if (!is.null(model_outputs$results_tables$Group_Expansion_Rates)) {
        out_tags <- append(out_tags, list(htmltools::HTML("**Calculated Group Rates**<br>")))
        dt_tbl <- DT::datatable(
          model_outputs$results_tables$Group_Expansion_Rates %>% mutate(across(where(is.numeric), ~round(., 5))),
          options = list(pageLength = 5, scrollX = TRUE), rownames = FALSE
        )
        out_tags <- append(out_tags, list(dt_tbl, htmltools::HTML("\n\n<br><br>\n\n")))
      }
      
      if (!is.null(model_outputs$results_tables$Model_Coefficients)) {
        out_tags <- append(out_tags, list(htmltools::HTML("**Model Coefficients**<br>")))
        dt_tbl_c <- DT::datatable(
          model_outputs$results_tables$Model_Coefficients %>% mutate(across(where(is.numeric), ~round(., 5))),
          options = list(pageLength = 5, scrollX = TRUE), rownames = FALSE
        )
        out_tags <- append(out_tags, list(dt_tbl_c, htmltools::HTML("\n\n<br><br>\n\n")))
      }
    } else {
      out_tags <- append(out_tags, list(htmltools::HTML("*No statistical tables found.*<br>")))
    }
  }
}

# Print the dynamically generated UI
htmltools::tagList(out_tags)
```

# Combined Analysis {.tabset .tabset-pills}

## Cross-Metric Correlation
This scatter plot compares the expansion rate (True BLUP Slope) of the Modal CAG length against the expansion rate of the Instability Index for each biological replicate. A strong positive correlation indicates that the clones expanding the fastest are also the ones becoming the most genetically unstable.

```{r cross-corr, out.width="100%"}
if (!is.null(all_plots$exploratory$p_cross_corr_mode_vs_iic)) {
  safe_plotly(all_plots$exploratory$p_cross_corr_mode_vs_iic)
} else {
  htmltools::HTML("<em>Cross-correlation plot not generated.</em>")
}
```

## Principal Component Analysis (PCA)
PCA reduces the dimensionality of the data to help identify overarching patterns, clusters, or batch effects across all measured variables simultaneously.

```{r pca-plots, out.width="100%"}
if (!is.null(all_plots$exploratory$p_biplot)) {
  htmltools::HTML("<h3>PCA Biplot</h3><p>Points represent individual replicates. Arrows represent the variables driving the separation.</p>")
  safe_plotly(all_plots$exploratory$p_biplot)
} else {
  htmltools::HTML("<em>PCA Biplot not available.</em>")
}

htmltools::HTML("<br><hr><br>")

if (!is.null(all_plots$exploratory$p_loadings_bars)) {
  htmltools::HTML("<h3>PCA Loadings</h3><p>Shows the contribution strength of each variable to the principal components.</p>")
  safe_plotly(all_plots$exploratory$p_loadings_bars)
}
```

## Correlation Matrix
Overview of the relationships between all measured variables across the dataset.

```{r corr-matrix, out.width="100%", fig.width=14, fig.height=14}
if (!is.null(all_plots$exploratory$p_corr_ggpairs_color)) {
  # ggpairs objects do not always convert cleanly to plotly, so we print the static image
  print(all_plots$exploratory$p_corr_ggpairs_color)
} else {
  htmltools::HTML("<em>Correlation matrix not available.</em>")
}
```
